Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-14 GEMDataSource.Rmd
Update GEMDataSource.Rmd
Difficulties with errors about text formatting that was fine 2 hours ago

---
title: "Education and the Rate of Entrepreneurship - Data Gathering and Analysis"
author: "Samuel Dundon and Thierry Racaud"
date: "November 14, 2014"
output: html_document
---
***

@@

In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM. Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants. To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection).

@@

The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey. PercentFear is:

>The Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.

@@

<br>
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

@@

To review, the three regression equations run for this assignment are the following:

@@

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}

@@

```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis'}

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis' }

@@

Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self-esteem a given education system is.

@@

Next steps will also include looking more thoroughly into control variables. To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.

>>>>

---
title: "Impact of Education on Entrepreneurship - Data Gathering and Analysis"
author: "Samuel Dundon and Thierry Racaud"
date: "November 14, 2014"
output: html_document
---
***

@@

In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM. Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants. To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).

@@

The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey. PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."

@@

<br>
```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

@@

To review, the three regression equations used for this assignment are included below.

@@

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}

@@

```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }

@@

Going forward, we are considering adding one oof the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.  Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.

@@

Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results. To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
